% ---------------
% based on http://en.wikibooks.org/wiki/LaTeX/Letters
% ------------
\documentclass[a4paper,12pt]{article}

\usepackage[utf8]{inputenc}
%\usepackage[spanish]{babel}
%\usepackage[portuguese]{babel}
\usepackage{setspace}
\onehalfspacing

\usepackage{color}
\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
\usepackage{hyperref}
%\usepackage[OT1]{fontenc}
%\usepackage{boisik}

%\usepackage[T1]{fontenc}
%\usepackage{PTSerifCaption} 

%\usepackage[T1]{fontenc}
%\usepackage{libertine}
%\renewcommand*\familydefault{\sfdefault}  %% Only if the base font of the document is to be sans serif

%\usepackage[LGR,T1]{fontenc} %% LGR encoding is needed for loading the package gfsneohellenic
%\usepackage[default]{gfsneohellenic}

%\usepackage[T1]{fontenc}
%\usepackage{lxfonts}

% \clubpenalty 10000
% \widowpenalty 10000
% \sloppy  % espaciamento entre palabras en una frase

%\usepackage[dvips]{graphicx}  % lo agregue para poder usar el dvips

\setlength\parindent{0pt}




% ====== MARGIN =========
\topmargin	15mm
\evensidemargin	-5mm
\textwidth	160mm
\textheight	250mm
\oddsidemargin	-5mm
% =======================

% \setlength{\parindent}{0.25in}

\bibliographystyle{elsarticle-num}

\begin{document}

\pagestyle{empty}


\vspace{5mm}

\begin{center}
Paper submission to the Journal of Computational Physics.
\end{center}

\vspace{5mm}

\begin{flushright}
Dublin, Ireland\\
\today
\end{flushright}


\begin{flushleft}
Prof.  Frederic G. Gibou, Prof. Dongbin Xiu\\
Editor board, Journal of Computational Physics\\
\end{flushleft}

\vspace{5mm}

We are pleased to submit our manuscript entitled ``A Jacobian-free Newton-Krylov method for high-order cell-centred finite volume solid mechanics'' for consideration in the Journal of Computational Physics.  The article was written by Ivan Batisti\'{c}, Pablo Castrillo and Philip Cardiff.

\vspace{5mm}

Motivated by the increasing interest in the engineering community in high-order methods for solid and fluid mechanics, and in line with recent studies presented in this journal by Nishikawa, Tsoutsanis and others, this work introduces third- and fourth-order cell-centred finite-volume schemes for solid mechanics, coupled with a Jacobian-free Newton–Krylov solver that eliminates the need to assemble complex Jacobians. By combining high-order accuracy, robustness on irregular meshes through an $\alpha$-stabilisation scheme, and computational efficiency, our methodology advances the application of finite-volume methods to solid mechanics and is particularly attractive for multiphysics simulations within unified finite-volume frameworks.
%
We believe the manuscript will interest readers focused on numerical methods, as it demonstrates a practical, high-performance approach that can be readily adopted in existing frameworks. All implementations are openly released in the solids4foam toolbox for OpenFOAM, promoting reproducibility and further research.



\vspace{5mm}

Finally, we remark that this is an original paper which has neither previously, nor simul-
taneously, been submitted anywhere else.

\vspace{5mm}
Thank you for considering our work. We look forward to your feedback.

\vspace{5mm}

Sincerely yours,

\vspace{2cm} 
Pablo Castrillo


\end{document}
